 

### 2021-06-15 vertical-thermal-review.Rmd
Update vertical-thermal-review.Rmd

In the face of global climate change, resiliency among forests also stand out, such as African rainforests, with canopy trees that are more resilient to warming and drought than other forests [@bennettResistanceAfricanTropical2021]. Increasing temperature acclimation among tropical, temperate and boreal species [@slotGeneralPatternsAcclimation2015;@slotPhotosyntheticPlasticityTropical2021; @wayJustRightTemperature2019; @cunninghamTemperateRainforestTrees2003] and recovery from canopy heat stress [@smithEmpiricalEvidenceResilience2020] are other mechanisms that will help forests cope with warming.

>>>>

In the face of global climate change, resiliency among forests also stand out, such as African rainforests, with canopy trees that are more resilient to warming and drought than other forests [@bennettResistanceAfricanTropical2021]. Increasing temperature acclimation among tropical, temperate and boreal species [@slotGeneralPatternsAcclimation2015; @slotPhotosyntheticPlasticityTropical2021; @wayJustRightTemperature2019; @cunninghamTemperateRainforestTrees2003; @cunninghamTemperateRainforestTrees2003] and recovery from canopy heat stress [@smithEmpiricalEvidenceResilience2020] are other mechanisms that will help forests cope with warming.
